DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/evaluation.tex
Revise evaluation figures

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{ Real-time performance of the Raspberry Pi 3 in processing 1000 frames.}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
    \hline
    \textbf{num cores} & \textbf{mean} & \textbf{max} & \textbf{99pct} & \textbf{stdev} \\ \hline 
    1 & 61.96 & 66.00 & 63.31 & 0.51\\ \hline
    2 & 50.49 & 71.55 & 70.03 & 4.18 \\ \hline
    3 & 48.11 & 72.22 & 58.45 & 2.80 \\ \hline
    4 & 42.67 & 56.37 & 50.70 & 2.80 \\
    \hline
  \end{tabular}
  \caption{Real-time performance of DeepPicar depending on the number of cores used.}
\end{table}

@@

\begin{table*}
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l |}
  \hline
  \textbf{num models} & \textbf{cores} & \textbf{mean} & \textbf{L1 refs} & \textbf{L1 
    misses} & \textbf{L1 miss \%} & \textbf{L2 refs} & \textbf{L2 misses} & \textbf{L2 miss \%} \\ \hline
  1 & 0,1 & 51.35 & 3.04E+10 & 4.78E+08 & 1.58 & 3.31E+09 & 3.68E+08 & 11.12\\ \hline
  2 & 0,1 & 58.03 & 3.04E+10 & 4.91E+08 & 1.61 & 3.91E+09 & 4.26E+08 & 10.88 \\ \hline
  2 & 2,3 & 56.40 & 3.04E+10 & 4.80E+08 & 1.58 & 3.88E+09 & 4.21E+08 & 10.87 \\ \hline
  \end{tabular}
  \caption{Real-time performance of the DeepPicar when 2 models are running simultaneously.}
\end{table*}

The results for the 2 model test are outlined in Table IV, and the 4 model test is summarized in Table 
V. In the the 2 model test, both of the models showed average inference time increases of around 5-7 
ms, $\sim$10\%, when compared to a baseline of 1 model running on two cores. The difference was even 
greater in the 4 model test, as each model displayed an average inference time increase of 
approximately 15 ms, $\sim$30\%, when compared to a single model running on 1 core.

@@

\begin{table*}
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l |}
  \hline
  \textbf{num models} & \textbf{core} & \textbf{mean} & \textbf{L1 refs} & \textbf{L1 
    misses} & \textbf{L1 miss \%} & \textbf{L2 refs} & \textbf{L2 misses} & \textbf{L2 miss \%} \\ \hline
    1 & 0 & 62.48 & 2.78E+10 & 4.36E+08 & 1.57 & 2.83E+09 & 3.59E+08 & 12.68 \\ \hline
    4 & 0 & 77.90 & 2.79E+10 & 4.53E+08 & 1.63 & 3.36E+09 & 4.43E+08 & 13.19 \\ \hline
    4 & 1 & 78.89 & 2.79E+10 & 4.64E+08 & 1.67 & 3.42E+09 & 4.38E+08 & 12.82 \\ \hline
    4 & 2 & 77.81 & 2.78E+10 & 4.45E+08 & 1.60 & 3.45E+09 & 4.41E+08 & 12.77 \\ \hline
    4 & 3 & 77.87 & 2.79E+10 & 4.45E+08 & 1.60 & 3.41E+09 & 4.39E+08 & 12.88 \\ \hline
  \end{tabular}
  \caption{Real-time performance of the DeepPicar when 4 models are running simultaneously.}
\end{table*}

@@

\subsection{Benchmark Performance}
In order to determine how cache misses affects the performance of the DeepPicar, we test its ability by 
running synthetic benchmarks concurrently with the model. In each experiment, we run a single model on a 
number of cores, and a synthetic benchmark on the remaining idle cores. The results of each test can be 
seen in Table VII.

\begin{table}[h]
\centering
  \begin{tabular} {| l | l | l | l | l | l |}
  \hline
  \textbf{num cores} & 1 & 2 & 3 \\ \hline
  \textbf{mean} & 562.33 & 391.98 & 98.05 \\ \hline
  \textbf{L1 refs} & 3.16E+10 & 3.17E+10 & 3.06E+10 \\ \hline
  \textbf{L1 misses} & 5.41E+08 & 5.35E+08 & 4.98E+08 \\ \hline
  \textbf{L1 miss \%} & 1.71 & 1.69 & 1.62 \\ \hline
  \textbf{L2 refs} & 3.49E+09 & 3.23E+09 & 3.21E+09 \\ \hline
  \textbf{L2 misses} & 8.05E+08 & 7.54E+08 & 4.98E+08 \\ \hline
  \textbf{L2 miss \%} & 23.05 & 23.37 & 15.51 \\ 
  \hline
  \end{tabular}
  \caption{Real-time performance of the DeepPicar when benchmarks are run concurrently with the model.}
\end{table}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{ Real-time performance of the DeepPicar in processing 1000 frames.}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
    \hline
    \textbf{num cores} & \textbf{mean} & \textbf{max} & \textbf{99pct} & \textbf{stdev} \\ \hline 
    1 & 61.96 & 66.00 & 63.31 & 0.51\\ \hline
    2 & 50.49 & 71.55 & 70.03 & 3.16 \\ \hline
    3 & 48.11 & 72.22 & 58.45 & 4.18 \\ \hline
    4 & 42.67 & 56.37 & 50.70 & 2.80 \\
    \hline
  \end{tabular}
  \caption{Real-time performance of DeepPicar depending on the number of cores used.}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/2ModelChart}
  \caption{ Change in inferencing time when 2 models are run concurrently. }
\end{figure}

\begin{table}[h]
\centering
  \begin{tabular} {| l | l | l |}
  \hline
  \textbf{num models} & 1 & 2 \\ \hline
  \textbf{L1 refs} &  3.04E+10 &  3.04E+10 \\ \hline
  \textbf{L1 misses} & 4.78E+08 & 4.91E+08 \\ \hline
  \textbf{L1 miss \%} & 1.58 & 1.61 \\ \hline
  \textbf{L2 refs} & 3.31E+09 &  3.91E+09 \\ \hline
  \textbf{L2 misses} & 3.68E+08 & 4.62E+08 \\ \hline
  \textbf{L2 miss \%} & 11.12 & 10.88 \\ \hline
  \end{tabular}
  \caption{ Effect of 2 simulatneous models on cache accesses. }
\end{table}

The results for the 2 model test are outlined in Figure 3 and Table IV, and the 4 model test is summarized in 
Figure 4 Table V. In the the 2 model test, both of the models showed average inference time increases of around 
5-7 ms, $\sim$10\%, when compared to a baseline of 1 model running on two cores. The difference was even 
greater in the 4 model test, as each model displayed an average inference time increase of 
approximately 15 ms, $\sim$30\%, when compared to a single model running on 1 core.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/4ModelChart}
  \caption{Change in inferencing time when 4 models are run simultaneously. }
\end{figure}

\begin{table}[h]
\centering
  \begin{tabular} {| l | l | l |}
  \hline
  \textbf{num models} & 1 & 4 \\  \hline
  \textbf{L1 refs} & 2.78E+10 & 2.79E+10 \\ \hline
  \textbf{L1 misses} & 4.36E+08 & 4.53E+08 \\ \hline
  \textbf{L1 miss \%} & 1.57 & 1.63 \\ \hline
  \textbf{L2 refs} & 2.83E+09 & 3.36E+09 \\ \hline 
  \textbf{L2 misses} & 3.59E+08 & 4.43E+08 \\ \hline
  \textbf{L2 miss \%} & 12.68 & 13.19 \\ 
\hline
  \end{tabular}
  \caption{ Effect of 4 concurrent models on cache accesses. }
\end{table}

@@

\subsection{Benchmark Performance}
In order to determine how cache misses affects the performance of the DeepPicar, we test its ability by 
running synthetic benchmarks concurrently with the model. In each experiment, we run a single model on a 
number of cores, and a synthetic benchmark on the remaining idle cores. The effects of the benchmarks can
seen in Figure 9 and Table VI.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/BenchmarkChart}
  \caption{ Effect of benchmarks on inferencing time. }
\end{figure}

\begin{table}[h]
\centering
  \begin{tabular} {| l | l | l | l | l | l |}
  \hline
  \textbf{num cores} & 1 & 2 & 3 \\ \hline
  \textbf{L1 refs} & 3.16E+10 & 3.17E+10 & 3.06E+10 \\ \hline
  \textbf{L1 misses} & 5.41E+08 & 5.35E+08 & 4.98E+08 \\ \hline
  \textbf{L1 miss \%} & 1.71 & 1.69 & 1.62 \\ \hline
  \textbf{L2 refs} & 3.49E+09 & 3.23E+09 & 3.21E+09 \\ \hline
  \textbf{L2 misses} & 8.05E+08 & 7.54E+08 & 4.98E+08 \\ \hline
  \textbf{L2 miss \%} & 23.05 & 23.37 & 15.51 \\ 
  \hline
  \end{tabular}
  \caption{ Effect of benchmarks on cache accesses. }
\end{table}
